Flabby and injective objects in toposes

### 2018-06-14 paper-flabby-objects.tex
Nicer wording of the definition of flabby objects

\begin{defn}An object~$X$ of an elementary topos~$\E$ is \emph{flabby} if and
only if it is a flabby set from the point of view of the internal language
of~$\E$.\end{defn}

This definition amounts to the following: An object~$X$ of an elementary
topos~$\E$ is flabby if and only if, for any object~$A$ of~$\E$, the object~$X'
\defeq X \times A \in \E/A$ has the following property:
\begin{quote}
For any monomorphism~$K \to 1$ in~$\E/A$ and any morphism~$K \to X'$%
\tikz[remember picture] \node[coordinate,yshift=0.7em,xshift=1.0em] (n1) {};
in~$\E/A$, there exists an epimorphism~$B \to 1$ in~$\E/A$ and a morphism~$B
\to X'$ in~$\E/A$ such that the following diagram commutes.
\end{quote}
\[ \xymatrix{
  K \times_A B \ar[r]\ar[rd] & X' \times_A B \ar[r] & X' \\
  & B \ar[ru]
} \]
\tikz[remember picture] \node[coordinate,yshift=0.3em] (n2) {};
\begin{tikzpicture}[overlay,remember picture]
  \path (n2) -| node[coordinate] (n3) {} (n1);
  \draw[thick,decorate,decoration={brace,amplitude=3pt}]
  (n1) -- (n3) node[midway, right=4pt] {$({\star})$};
\end{tikzpicture}

Instead of referencing arbitrary stages~$A \in \E$, one can also just reference
the generic stage: Let~$\P_{\leq1}(X)$ denote the \emph{object of subterminals}
of~$X$; this object is a certain suboject of~$\P(X) = [X,\Omega_\E]_\E$, the
powerobject of~$X$. The subobject~$K$ of~$\P_{\leq1}(X) \times X$ classified by the
evaluation morphism~$\P_{\leq1}(X) \times X \to \P(X) \times X \to \Omega_\E$
is the \emph{generic subterminal} of~$X$. The object~$X$ is flabby if and only
if there exists an epimorphism~$B \to \P_{\leq1}(X)$ and a morphism~$B \to X$
such that the following diagram commutes.
\[ \xymatrix{
  K \times_{\P_{\leq1}(X)} B \ar[r]\ar[rd] & X \times B \ar[r] & X \\
  & B \ar[ru]
} \]

>>>>

\begin{defn}An object~$X$ of an elementary topos~$\E$ is \emph{flabby} if and
only if the statement~``$X$ is a flabby set'' holds in the stack semantics
of~$\E$.\end{defn}

This definition amounts to the following: An object~$X$ of an elementary
topos~$\E$ is flabby if and only if, for any monomorphism~$K \to A$ and any
morphism~$K \to X$, there exists an epimorphism~$B \to A$ and a morphism~$B
\to X$ such that the following diagram commutes.
\[ \xymatrix{
  K \times_A B \ar@{^{(}->}[r]\ar[d] & B \ar@{-->}@/^/[ld] \\
  X
} \]

Instead of referencing arbitrary stages~$A \in \E$, one can also just reference
the generic stage: Let~$\P_{\leq1}(X)$ denote the \emph{object of subterminals}
of~$X$; this object is a certain suboject of~$\P(X) = [X,\Omega_\E]_\E$, the
powerobject of~$X$. The subobject~$K_0$ of~$\P_{\leq1}(X) \times X$ classified by the
evaluation morphism~$\P_{\leq1}(X) \times X \to \P(X) \times X \to \Omega_\E$
is the \emph{generic subterminal} of~$X$. The object~$X$ is flabby if and only
if there exists an epimorphism~$B \to \P_{\leq1}(X)$ and a morphism~$B \to X$
such that the following diagram commutes.
\[ \xymatrix{
  K_0 \times_{\P_{\leq1}(X)} B \ar@{^{(}->}[r]\ar[d] & \P_{\leq1}(X) \ar@{-->}@/^/[ld] \\
  X
} \]

\begin{prop}\label{prop:basic-properties-of-flabby-objects}
Let~$X$ and~$T$ be objects of an elementary topos~$\E$.
\begin{enumerate}
\item If~$X$ is flabby, so is~$X \times T$ as an object in~$\E/T$.
\item The converse holds if the unique morphism~$T \to 1$ is an epimorphism.
\end{enumerate}
\end{prop}

\begin{proof}These properties are shared by any property which can be defined
in the stack semantics~\cite[Lemma~7.3]{shulman:stack-semantics}.
\end{proof}
